### 2011-08-17 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress.

\subsubsection{Linux Machine}

\begin{verbatim}
Intel Core 2 Quad processor @ 2.83 GHz
8 GB DDR2 RAM
x86_64 GNU/Linux 2.6.32-33-generic Ubuntu 10.04
Java SE Runtime Environment (build 1.6.0_26-b03)
Java HotSpot 64-Bit Server VM (build 20.1-b02)
GLPK version 4.38
\end{verbatim}

\subsubsection{Windows Machine}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data        & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data        & all sized test data sets \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data set    & all official test data sets \\
  Iterations        & 1 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

>>>>

\subsubsection{Quad Core Machine}

\begin{verbatim}
Intel Core 2 Quad processor @ 2.83 GHz
8 GB DDR2 RAM
Windows 7 SP1 64bit
TODO
TODO
GLPK version TODO
\end{verbatim}

\subsubsection{Dual Core Machine}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & all sized test data sets \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data set    & all official test data sets \\
  Iterations        & 1 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}
